Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-05-30 writeup/gz_hubble_data.tex
ApJ bst file
Funding for @rjsmethurst.
Moved tables to separate files.

\documentclass[twocolumn]{aastex6}

%% The other main article choice is a tightly typeset, two-column article
%% that more closely resembles the final typeset pdf article.
%%
%% \documentclass[twocolumn]{aastex6}
%% 
%% There are other optional arguments one can invoke to allow other 
%% actions. 
%%
% These are the available options:
%   manuscript  : onecolumn, doublespace, 12pt fonts
%   preprint    : onecolumn, single space, 10pt fonts
%   preprint2   : twocolumn, single space, 10pt fonts
%   twocolumn   : a two column article. Probably not needed, but here just in case.
%   onecolumn   : a one column article; default option.
%   twocolappendix: make 2 column appendix
%   onecolappendix: make 1 column appendix is the default. 
%   astrosymb   : Loads Astrosymb font and define \astrocommands. 
%   tighten : Makes baselineskip slightly smaller
%   times   : uses times font instead of the default
%   linenumbers : turn on lineno package.
%   trackchanges : required to see the revision mark up and print output
%   numberedappendix: Labels appendix sections A, B, ... This is the default.
%   appendixfloats: Needed. Resets figure and table counters to zero

%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,twocolappendix,linenumbers,trackchanges]{aastex6}

\shorttitle{Galaxy Zoo: Hubble}
\shortauthors{Willett et al.}

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

\usepackage{epsfig}
\usepackage{color,soul}
\usepackage{natbib}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{url}
\usepackage[normalem]{ulem}
\bibliographystyle{mn2e}

@@

\begin{document}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire.

\title{Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging}
%% Use \author, \affil, plus the \and command to format author and affiliation 
%% information.  If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.
%%
%% The \affil should be used to document primary affiliations and the
%% \altaffil should be used for secondary affiliations, titles, or email.

%% Authors with the same affiliation can be grouped in a single
%% \author and \affil call.
\author{
    Kyle W. Willett\altaffilmark{1,2}, 
    Melanie A. Galloway\altaffilmark{1}, 
    Steven P. Bamford\altaffilmark{3}, 
    Chris J. Lintott\altaffilmark{4}, 
    Karen L. Masters\altaffilmark{5,6}, 
    Claudia Scarlata\altaffilmark{1}, 
    B.D. Simmons\altaffilmark{4,7}, 
    Melanie Beck\altaffilmark{1}, 
    Carolin N. Cardamone\altaffilmark{8}, 
    Edmond Cheung\altaffilmark{9}, 
    Edward M. Edmondson\altaffilmark{5}, 
    Lucy F. Fortson\altaffilmark{1},
    Roger L. Griffith\altaffilmark{10,11}, 
    Boris H\"au{\ss}ler\altaffilmark{4,12,13},
    Anna Han\altaffilmark{14}, 
    Ross Hart\altaffilmark{3}, 
    Thomas Melvin\altaffilmark{5}, 
    Michael Parrish\altaffilmark{15}, 
    Kevin Schawinski\altaffilmark{16}, 
    R.J. Smethurst\altaffilmark{4}, 
    Arfon M. Smith\altaffilmark{4,15,17}
}
%
%$^N$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
%$^N$South East Physics Network, www.sepnet.ac.uk\\
%$^N$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
%$^N$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
%$^N$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
%$^N$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
%$^N$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tucson, AZ 85721, USA\\
%$^N$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
%$^N$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
%$^N$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
%$^N$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
%$^N$Einstein Fellow\\

\altaffiltext{1}{School of Physics and Astronomy, University of Minnesota, 116 Church St. SE, Minneapolis, MN 55455, USA}
\altaffiltext{2}{Department of Physics and Astronomy, University of Kentucky, 505 Rose St., Lexington, KY 40506, USA}
\altaffiltext{3}{School of Physics and Astronomy, The University of Nottingham, University Park, Nottingham, NG7 2RD, UK}
\altaffiltext{4}{Oxford Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK}
\altaffiltext{5}{Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK}
\altaffiltext{6}{SEPnet, South East Physics Network, UK}
\altaffiltext{7}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, San Diego, CA 92093, USA}
\altaffiltext{8}{Department of Mathematics and Science, Wheelock College, Boston, MA 02215, USA}
\altaffiltext{9}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), Todai Institutes for Advanced Study, The University of Tokyo, Kashiwa 277-8583, Japan}
\altaffiltext{10}{Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA}
\altaffiltext{11}{Department of Astronomy \& Astrophysics, 525 Davey Lab, The Pennsylvania State University, University Park, PA 16802, USA}
\altaffiltext{12}{Centre for Astrophysics, Science \& Technology Research Institute, University of Hertfordshire, Hatfield, AL10 9AB, UK}
\altaffiltext{13}{European Southern Observatory, Alonso de C\'ordova 3107, Vitacura, Casilla 19001, Santiago, Chile}
\altaffiltext{14}{Department of Astronomy, Yale University, New Haven, CT 06520, USA}
\altaffiltext{15}{Adler Planetarium, 1300 S. Lake Shore Drive, Chicago, IL 60605, USA}
\altaffiltext{16}{Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland}
\altaffiltext{17}{GitHub}

\begin{abstract}

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
were selected from various publicly-released \textit{Hubble Space Telescope}
Legacy programs using the Advanced Camera for Surveys, with filters that probe
the rest-frame optical emission from galaxies out to $z\sim1$.  The bulk of the
sample is selected to have $m_{I814W}<23.5$, but goes as faint as
$m_{I814W}<26.8$ for deep images combined over 5~epochs. The median redshift of
the combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out
to $z\simeq4$. The GZH morphological data include measurements of both bulge-
and disk-dominated galaxies, details on spiral disk structure that relate to
the Hubble type, bar identification, and numerous measurements of clump
identification and geometry.  This paper also describes a new method for
calibrating morphologies for galaxies of different luminosities and at
different redshifts by using artificially-redshifted galaxy images as a
baseline. The GZH catalog contains both raw and calibrated morphological vote
fractions for $119,849$~galaxies, providing the largest dataset to date
suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
% Number = hubble + goods_shallow + stripe82_coadd
\end{abstract}

\keywords{galaxies:structure --- galaxies:high redshift --- galaxies:evolution
--- methods:data analysis --- catalogs}

\section{Introduction} \label{sec:intro}

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \hst{} Advanced Camera for
Surveys (ACS) in wide-field channel mode for the various surveys in GZH. The
unfilled black curves show the filters for the Suprime Camera on \subaru, which
was used to create color gradients in the GZH COSMOS
images.\label{fig:filtercurves}}
\end{figure*}

@@

Two sets of simulated AGN were generated in GZH. The first set (version~1) was
assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by
combining stars in the GOODS fields using the PSF creation tools in
\texttt{daophot}.  The second set (version~2) was assembled from 96~galaxies in
GOODS-S; this version used simulated PSFs from \texttt{TinyTim} \citep{kri93},
drizzled using the same procedures as those used in the reduction of the GOODS-S
images \citep{koe02,koe03,gia04}. The use of these two versions facilitates
comparisons between these different PSF creation methods, which are widely used
in AGN host galaxy morphology studies
\citep[e.g.,][]{san04,sim08,pie10a,simm11}.  Each PSF creation method has
advantages and disadvantages: the empirical PSFs better represent the nuances
of the PSF in the specific data being used and look more realistic at lower
luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs
are visually more realistic at higher luminosities.
% okay so I'm a cheeky self-citing biyotch

@@

%\begin{table*}
%\center
%\caption{Summary of morphological categories selected for \ferengi{} sample.\label{tbl:morphologies}}
%\begin{tabular}{lllc}
%\hline\hline
%Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
%                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
%\hline
%Features            & Yes       & $f_{\rm features} > 0.8$, $f_{\rm odd} < 0.1$                                                         & 12 \\ 
%                    & Int.      & $0.3 < f_{\rm smooth} < 0.6$, $f_{\rm odd} < 0.1$                                                     & 12 \\ 
%                    & No        & $f_{\rm smooth} > 0.8$, $f_{\rm odd} < 0.1$                                                           & 12 \\ 
%Merger              & No        & $f_{\rm features} > 0.8$, $f_{\rm odd < 0.1}$, $f_{\rm merger} < 0.1$                                 & 12 \\
%                    & Int.      & $f_{\rm odd} > 0.5$, $0.1< f_{\rm merger} < 0.4$                                                      & 12 \\ 
%                    & Yes       & $f_{\rm odd} > 0.5$, $f_{\rm merger} > 0.4$                                                           & 12 \\
%Edge-on             & Yes       & $f_{\rm edgeon} > 0.8$, $f_{\rm features} > 0.5$                                                      & 12 \\
%                    & Int.      & $0.4 < f_{\rm edgeon} < 0.8$ , $f_{\rm features} > 0.5$                                               & 12 \\
%                    & No        & $f_{\rm edgeon} < 0.2$, $f_{\rm features} > 0.5$                                                      & 12 \\
%Bar                 & No        & $f_{\rm bar} < 0.1$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
%                    & Int.      & $0.2 < f_{\rm bar} < 0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                           & 24 \\
%                    & Yes       & $f_{\rm bar} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$                                 & 24 \\
%Visible spiral      & No        & $f_{\rm spiral} < 0.2$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
%                    & Int.      & $0.2 < f_{\rm spiral} < 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$   & 12 \\
%                    & Yes       & $f_{\rm spiral} > 0.8$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.2$, $f_{\rm bar} < 0.1$         & 12 \\
%Oblique bulge size  & No        & $f_{\rm nobulge>0.6}$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$          & 12 \\
%                    & Int.      & $f_{\rm justnoticeable}>0.6$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$   & 12 \\
%                    & Yes       & $f_{\rm obvious|dominant}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} < 0.5$, $f_{\rm bar} < 0.2$ & 12 \\
%Edge-on bulge shape & Round     & $f_{\rm rounded}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
%                    & Boxy      & $f_{\rm boxy}>0.4$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.2$                                  & 12 \\
%                    & No bulge  & $f_{\rm nobulge}>0.5$, $f_{\rm features} > 0.5$, $f_{\rm edgeon} > 0.5$                               & 12 \\
%\hline\hline
%\end{tabular}
%\end{table*}

@@

%\begin{table}
%\caption{Summary of \ferengi{} artificial redshifting \label{tbl:ferengivalues}}
%\begin{tabular}{lccccr}
%\hline\hline
%$z_{\rm sim}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
%\hline
%0.3              & 8                  & 7                   & $-3.0$        & 72             & 4032 \\
%0.5              & 6                  & 4                   & $-1.5$        & 72             & 1728 \\
%0.8              & 3                  & 3                   & $-1.0$        & 72             &  648 \\
%1.0              & 1                  & 3                   & $-1.0$        & 72             &  216 \\
%\hline\hline
%\end{tabular}
%\end{table}

@@

In addition to the primary \hst{} legacy imaging sample with colored images
described as above, GZH also includes samples of \hst{} galaxy images with
different color prescriptions. In particular, there are two sets of 3,927~images
each, drawn from the COSMOS sample; the first has a dramatically reduced color
saturation, and the second has reversed the colors so that the blue and red
filters have exchanged places in the RGB image. The `faded' galaxy set
facilitates measuring of possible variations in classification due to the
presence or absence of color features. The `recolored' set enables an
alternative test of potential color biases in classifications.
% I guess this means we need to say somewhere later that we don't see an effect
% (we don't, right?).  Would also be good to cite here where we have done
% similar things in the past...

The simulated AGN host galaxy color images (described in Section \ref{ssec:sim_agn})
were created using the same prescription as for the GOODS 2-epoch imaging. The
artificially redshifted color images (Section \ref{ssec:ferengi}) were created using the
same prescription as for the AEGIS images.
% Edmond should verify the AEGIS bit above.

@@

%\tabletypesize{\scriptsize}
%\begin{deluxetable*}{l|rr|rrr|rr|r|rr}
%\tablecolumns{12}
%\tablewidth{0pc}
%\tablecaption{GZH redshifts by survey\label{tbl:redshifts}} 
%\tabletypesize{\scriptsize}
%\tablehead{
% &   
%\multicolumn{2}{c}{\underline{ACS-GC}} &
%\multicolumn{3}{c}{\underline{3DHST}} &
%\multicolumn{2}{c}{\underline{MUSYC}} &
%\multicolumn{1}{c}{\underline{UltraVISTA}}&
%\multicolumn{2}{c}{\underline{Total}} 
%\\
%\colhead{Survey} & 
%\colhead{spec-z} & 
%\colhead{photo-z} & 
%\colhead{spec-z} & 
%\colhead{grism-z} & 
%\colhead{photo-z} & 
%\colhead{spec-z} & 
%\colhead{photo-z} & 
%\colhead{photo-z} & 
%\colhead{with redshift} &
%\colhead{in survey}
%}
%\small
%\startdata
%%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
%AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373   & 8,507   \\
%COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020  & 92,808  \\
%GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743   & 9,304   \\
%GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328   & 12,030  \\
%GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040   & 10,284  \\
%SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545  & 51,861  \\
%\hline
%Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794 \\
%\enddata
%\end{deluxetable*}

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/gzh_interface.png}
\caption{Screenshot of the GZH interface (\url{http:/zoo3.galaxyzoo.org}) at
the beginning of classifying a random galaxy, with the classifier ready
to select an answer for the first question in the decision
tree.\label{fig:interface}}
\end{figure*}

@@

\begin{table}
\center
\caption{Distribution of \ferengi{} images analyzed in Figure~\ref{fig:f_vs_f}.
Correctable images have a single-valued relationship between their measured
\ffeatures{} values at high and low redshifts (white regions in
Figure~\ref{fig:f_vs_f}). Images with only a lower-limit on \ffeatures{} have a
non single-valued relationship (blue regions). NEI (``not enough information'')
images have undetermined relationships due to a lack of data ($N<5$) in their
corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
                                   & N       & \% \\
\hline 
Correctable                        & 1,690   &  49\% \\
Lower-limit                        & 1,678   &  49\% \\
NEI                                & 81      &   2\%\\
Total                              & 3,449   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrlllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for \hst{} images from AEGIS, COSMOS, GEMS, and GOODS\label{tbl:catalog_hst}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Zooniverse ID} & 
\colhead{Survey ID} & 
\colhead{Imaging} & 
\colhead{Correction$^{1}$} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{flag} &
\colhead{}
}
\small
\startdata
AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226 & 0  \\
AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$   & 0  \\
$\ldots$    \\
AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$   & 0  \\
AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$   & 0  \\
$\ldots$    \\
AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800 & 0  \\
AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727 & 0  \\
$\ldots$    \\
AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496 & 0  \\
AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669 & 0  \\
$\ldots$    \\
AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548 & 0  \\
AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287 & 0  \\
$\ldots$    \\
\enddata
\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were
corrected through debiasing (Section~\ref{ssec:zeta_results}), if possible.
0~=~correctable, 1~=~lower-limit ($f_\mathrm{raw}$ --- $f_\mathrm{adj}$ is not
single-valued), 2~=~uncorrected ($z < 0.3$), 3~=~uncorrected
(insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no
galaxy redshift available).}
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 113,705~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrlllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for color-faded \hst{} images\label{tbl:catalog_faded}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Zooniverse ID} & 
\colhead{Survey ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{flag} &
\colhead{}
}
\small
\startdata
AHZF000001  &   20000002    &   COSMOS  &   1   &   48 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325   &   0.829 & 0 \\
AHZF000003  &   20000004    &   COSMOS  &   3   &   49 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198   &   0.198 & 0 \\
AHZF000004  &   20000006    &   COSMOS  &   3   &   49 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$     &   $-$   & 0 \\
AHZF00000z  &   20000102    &   COSMOS  &   1   &   44 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316   &   0.820 & 0 \\
AHZF000010  &   20000104    &   COSMOS  &   2   &   53 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$     &   $-$   & 0 \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 3,927~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}

%\usepackage{epsfig}
\usepackage{color,soul}
%\usepackage{natbib}
\usepackage{deluxetable}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{url}
%\usepackage[normalem]{ulem}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

@@

\title[Galaxy Zoo: Hubble]{Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging}

\author[Willett et al.]{
Kyle W. Willett$^{1,2}$,
Melanie A. Galloway$^{1}$,
Steven P. Bamford$^{3}$,
Chris J. Lintott$^{4}$,
\newauthor
Karen L. Masters$^{5,6}$,
Claudia Scarlata$^{1}$,
B.D. Simmons$^{4,7}$\footnote{Einstein Fellow},
Melanie Beck$^{1}$,
\newauthor
Carolin N. Cardamone$^{8}$,
Edmond Cheung$^{9}$,
Edward M. Edmondson$^{5}$,
Lucy F. Fortson$^{1}$,
\newauthor
Roger L. Griffith$^{10,11}$,
Boris H\"au{\ss}ler$^{4,12,13}$,
Anna Han$^{14}$,
Ross Hart$^{3}$,
\newauthor
Thomas Melvin$^{5}$,
Michael Parrish$^{15}$,
Kevin Schawinski$^{16}$,
R.J. Smethurst$^{4}$,
\newauthor
Arfon M. Smith$^{4,15,17}$
\\
%
$^{1}$School of Physics and Astronomy, University of Minnesota, 116 Church St. SE, Minneapolis, MN 55455, USA \\
$^{2}$Department of Physics and Astronomy, University of Kentucky, 505 Rose St., Lexington, KY 40506, USA \\
$^{3}$School of Physics and Astronomy, The University of Nottingham, University Park, Nottingham, NG7 2RD, UK \\
$^{4}$Oxford Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK \\
$^{5}$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
$^{6}$SEPnet, South East Physics Network, UK \\
$^{7}$Center for Astrophysics and Space Sciences, Department of Physics, University of California, San Diego, CA 92093, USA \\
$^{8}$Department of Mathematics and Science, Wheelock College, Boston, MA 02215, USA \\
$^{9}$Kavli Institute for the Physics and Mathematics of the Universe (WPI), \\ Todai Institutes for Advanced Study, The University of Tokyo, Kashiwa 277-8583, Japan \\
$^{10}$Infrared Processing and Analysis Center, California Institute of Technology, Pasadena, CA 91125, USA \\
$^{11}$Department of Astronomy \& Astrophysics, 525 Davey Lab, The Pennsylvania State University, University Park, PA 16802, USA \\
$^{12}$Centre for Astrophysics, Science \& Technology Research Institute, University of Hertfordshire, Hatfield, AL10 9AB, UK \\
$^{13}$European Southern Observatory, Alonso de C\'ordova 3107, Vitacura, Casilla 19001, Santiago, Chile \\
$^{14}$Department of Astronomy, Yale University, New Haven, CT 06520, USA \\
$^{15}$Adler Planetarium, 1300 S. Lake Shore Drive, Chicago, IL 60605, USA \\
$^{16}$Institute for Astronomy, Department of Physics, ETH Z\"urich, Wolfgang-Pauli-Strasse 27, CH-8093 Z\"urich, Switzerland \\
$^{17}$GitHub
}

\date{Accepted XXX. Received YYY; in original form ZZZ}
\pubyear{2016}

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

\begin{abstract}
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
were selected from various publicly-released \textit{Hubble Space Telescope}
Legacy programs using the Advanced Camera for Surveys, with filters that probe
the rest-frame optical emission from galaxies out to $z\sim1$.  The bulk of the
sample is selected to have $m_{I814W}<23.5$, but goes as faint as
$m_{I814W}<26.8$ for deep images combined over 5~epochs. The median redshift of
the combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out
to $z\simeq4$. The GZH morphological data include measurements of both bulge-
and disk-dominated galaxies, details on spiral disk structure that relate to
the Hubble type, bar identification, and numerous measurements of clump
identification and geometry.  This paper also describes a new method for
calibrating morphologies for galaxies of different luminosities and at
different redshifts by using artificially-redshifted galaxy images as a
baseline. The GZH catalog contains both raw and calibrated morphological vote
fractions for $119,849$~galaxies, providing the largest dataset to date
suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
% Number = hubble + goods_shallow + stripe82_coadd
\end{abstract}

\begin{keywords}
galaxies:structure --- galaxies:high redshift --- galaxies:evolution
--- methods:data analysis --- catalogs
\end{keywords}

\section{Introduction}\label{sec:intro}

@@

\begin{figure*}
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \hst{} Advanced Camera for
Surveys (ACS) in wide-field channel mode for the various surveys in GZH. The
unfilled black curves show the filters for the Suprime Camera on \subaru, which
was used to create color gradients in the GZH COSMOS
images.}
\label{fig:filtercurves}
\end{figure*}

@@

Two sets of simulated AGN were generated in GZH. The first set (version~1) was
assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by
combining stars in the GOODS fields using the PSF creation tools in
\texttt{daophot}.  The second set (version~2) was assembled from 96~galaxies in
GOODS-S; this version used simulated PSFs from \texttt{TinyTim} \citep{kri93},
drizzled using the same procedures as those used in the reduction of the GOODS-S
images \citep{koe02,koe03,gia04}. The use of these two versions facilitates
comparisons between these different PSF creation methods, which are widely used
in AGN host galaxy morphology studies
\citep[e.g.,][]{san04,sim08,pie10a,simm11}.  Each PSF creation method has
advantages and disadvantages: the empirical PSFs better represent the nuances
of the PSF in the specific data being used and look more realistic at lower
luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs
are visually more realistic at higher luminosities.
% okay so I'm a cheeky self-citing biyotch - BDS

@@

%\input{tables/morphologies.tex}

@@

%\input{tables/ferengi.tex}

@@

In addition to the primary \hst{} legacy imaging sample with colored images
described as above, GZH also includes samples of \hst{} galaxy images with
different color prescriptions. In particular, there are two sets of 3,927~images
each, drawn from the COSMOS sample; the first has a dramatically reduced color
saturation, and the second has reversed the colors so that the blue and red
filters have exchanged places in the RGB image. The `faded' galaxy set
facilitates measuring of possible variations in classification due to the
presence or absence of color features. The `recolored' set enables an
alternative test of potential color biases in classifications.
% I guess this means we need to say somewhere later that we don't see an effect
% (we don't, right?).  Would also be good to cite here where we have done
% similar things in the past... - BDS

The simulated AGN host galaxy color images (described in Section \ref{ssec:sim_agn})
were created using the same prescription as for the GOODS 2-epoch imaging. The
artificially redshifted color images (Section \ref{ssec:ferengi}) were created using the
same prescription as for the AEGIS images.
% Edmond should verify the AEGIS bit above. - BDS

@@

%\input{tables/redshifts.tex}

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/gzh_interface.png}
\caption{Screenshot of the GZH interface at
the beginning of classifying a random galaxy, with the classifier ready
to select an answer for the first question in the decision
tree.\label{fig:interface}}
\end{figure*}

@@

\begin{table}
\center
\caption{Distribution of the ability of images to measure
morphological bias for
the \ferengi{} data (see Figure~\ref{fig:f_vs_f}).}
\label{tbl:ferengi_corrections}
\begin{tabular}{lrr}
\hline \hline
                                   & N       & \% \\
\hline 
Correctable                        & 1,690   &  49\% \\
Lower-limit                        & 1,678   &  49\% \\
NEI                                & 81      &   2\%\\
Total                              & 3,449   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

\clearpage
\input{tables/main.tex}
\input{tables/faded.tex}
\input{tables/recolored.tex}
\input{tables/goods-shallow.tex}
\clearpage
\input{tables/stripe82-single.tex}
\input{tables/stripe82-coadded.tex}
\input{tables/simulated-agn.tex}
\clearpage
